\chapter*{Acknowledgements}  

{\small I am so thankful to have been able to spend four years wandering rivers and chasing waterfalls in the company of amazing people. To my supervisors, Ian Donohue and Celia Holland, I could not have asked for a better team to guide me. Ian, your encouragement and trust have meant the world to me. Thank you for patiently listening to my ideas and allowing me the freedom to explore new avenues. Celia, your love for parasites infected me as an undergraduate and your kindness and thoughtfulness have buoyed me through even the roughest seas. Thank you for every long chat over coffee, for putting my welfare first, and for trusting me throughout. I am so lucky to have learned from you both; it really has been a dream team.}

{\small To the members of T.C.D. Zoology, you have made this thesis possible.  A special thank you to my committee, Yvonne and Andrew, for their feedback along the way. Thanks to Alison, who never turned me away even when I had the craziest of schemes. To Peter Stafford, Fiona Moloney, and Sarah-Louise Hassett, thank you so much for all of your support. Thank you to Andrew Jackson, who was always next door and there whether I needed a laugh or serious support. A major thank you to the Festive Office, Andrew Mooney and Alain Finn, who made sure every day was a great day. To Sam, Ruth, and Paula, thank you for all the meaningful chats, helpful feedback, and sunshine you brought to my days. To Darren, thank you for all the late night chats and laughs; I'm so glad you were my cohort. To Deirdre, I honestly would not have been able to do any of this without you. From my IRC application to the final hand in, your care and support has meant the world to me.}

{\small To all of the undergradutes and interns I have had the immense pleasure of working with, thank you a million times over. Thank you for trusting me, helping me, and putting your hearts into the team. The \#GamFam (Josh, Laura, Caoimhe, Paula, Sarah, Amy, Megan, Eoin, Floriane, Áine, Áine, Jeremie, Meg, Michelle, Jerome, Alice, Shannon, Casey, and Juliette) truly made all of this possible. Thank you to all those who helped in the field and in the lab; teamwork makes the dream work and this whole thesis is thanks to your hard work.

{\small To those outside of academia who have made the past four years exceptional, I am so grateful. To Adventure Club and the members of DUSAC, thank you for the endless pints of Guinness, sips of Mickey Finns, lady pong, adventure races, dives, hikes, and cycles. The adventure really was our friendship this whole time. To Eve Kearney, thank you for all the late nights and belly laughs. To Katie Still, I would not have been able to do this without your constant support and I will treasure every memory from these four years, including our Crazy Eyes Road Trips belting the Backstreet Boys. To my Floridians and my Domers, thank you for all the love all the way across the Atlantic.}

{\small To Pat, Col, and Matt, the original BSO crew, and all of the Fogarty and Williams families, I am so lucky to have the world's most supportive family network. Thanks to my brother, Matthew, who never fails to cheer me up and encourages me to do things I did not think I could. To my father, Ed, thank you kindling in me a love of nature and supporting me every step of the way. To my mother, Anne, thank you for every late night, every phone call, every Sunday Skype, every lift to school or practice, and every time you listened to my worries and dreams. I will always cherish our adventures together.}