\chapter*{Acknowledgements}  
\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{quoteshrink}
  ``In this universe we are given two gifts: the ability to love, and the ability to ask questions.''

\hfill{Mary Oliver}
\end{quoteshrink}

{\small I am so thankful to have been able to spend four years wandering rivers and asking questions in the company of amazing people. Thanks firstly to my supervisors, Ian Donohue and Celia Holland. Ian, your encouragement and trust have meant the world to me. Thank you for patiently listening to my ideas and allowing me the freedom to explore new avenues. Celia, your love for parasites infected me as an undergraduate and your kindness and thoughtfulness have buoyed me through even the roughest seas. Thank you for every long chat over coffee. I am so lucky to have learned from you both; it really has been a dream team.}

{\small A special thank you to the members of T.C.D. Zoology and NERD club, especially my committee, Yvonne Buckley and Andrew Jackson, for their feedback along the way. Thanks to Alison Boyce, who never turned me away even when I had the craziest of schemes. To Peter Stafford, Fiona Moloney, and Sarah-Louise Hassett, thank you so much for all of your support. Thanks particularly to Andrew Jackson, who was always next door and there whether I needed a laugh or serious support. A major thank you to the Festive Office, Andrew Mooney and Alain Finn, who made sure every day was a great day. To Sam, Ruth, Aoibheann, and Paula, thank you for all the meaningful chats, helpful feedback, and sunshine you brought to my days. To Darren, thank you for all the late night chats and laughs; I'm so glad you were my cohort. To Deirdre, I honestly would not have been able to do any of this without you. From my IRC application to the final hand in, your care and support has meant the world to me.}

{\small To all of the undergradutes and interns I have had the immense pleasure of working with, thank you a million times over for trusting me, helping me, and putting your hearts into the team. The \#GamFam (Josh, Laura, Caoimhe, Paula, Sarah, Amy, Megan, Eoin, Floriane, Áine G, Áine N, Jeremie, Meg, Michelle, Jerome, Alice, Shannon, Casey, and Juliette) truly made all of this possible. Thank you to all who helped in the field and in the lab; teamwork made this dream work.}

{\small To Adventure Club and the members of DUSAC, thank you for the endless pints of Guinness, sips of Mickey Finns, lady pong, adventure races, dives, hikes, and cycles. Turns out the adventure really was our friendship this whole time. To Eve Kearney, thank you for all the late nights and belly laughs. To Katie Still, I would not have been able to do this without your constant support and all the Crazy Eyes Road Trips belting the Backstreet Boys. To my Floridians and Domers, thank you for all the love all the way across the Atlantic.}

{\small To the original BSO crew, and all of the Fogarty and Williams families, I am so lucky to have the world's most supportive family network. To my Godmother Marlene, thank you for all the cards and love. Thanks to my brother, Matthew, who never fails to cheer me up and is always there for a cold beer or a phone call. To my father, Edward, thank you kindling in me a love of nature and supporting me every step of the way. To my mother, Anne, thank you for every late night, every phone call, every Sunday Skype, every lift to school or practice, and every time you listened to my worries and dreams.} 

{\small I will always cherish our adventures together.}