\chapter*{Specific chapter acknowledgements}
\addcontentsline{toc}{chapter}{Additional information for each specific chapter}

\section*{Contributions}
For each chapter, I designed the experiments, ran the analyses, interpreted the results, and wrote the manuscripts. Ian Donohue and Celia Holland assisted in designing the experiments and writing the manuscripts.

\section*{Specific acknowledgements}

\subsection*{Warming can alter host behaviour to the same extent as behaviour-manipulating parasites}
Thanks to Paula Tierney, Jérôme Raimbault, and Michelle Kim for their assistance with data collection, and Ruth Kelly, Marcin Penk, and Kevin Healy for their help with analyses. 

\subsection*{Infection with behaviour-manipulating parasites enhances bioturbation by key aquatic detritivores}
Thanks to Alison Boyce who help with experimental chamber design. Thanks to Daniel Wohlgemuth and Floriane O'Keefe for their help with method development. A final thanks to Juliette Piccard who was instrumental in setting up the experiment.

\subsection*{The temperature-dependence and influence of prey mobility on multiple components of handling time}
Thanks to Juliette Piccard, Casey Patmore, and Shannon Weldon, who assited with trial observations. Thanks to Nicola Marples and Anthony Dell for their help in experimental design and analyses.

\subsection*{Individual and combined effects of warming, intraspecific competition and parasitic infection on detritus processing rates \emph{in situ}}
Thanks to Aine Gavin, Floriane O'Keefe, Juliette Piccard, and Marcin Penk for all their assistance in the lab and the field.
